formula1

### 2020-06-07 inst/f1points.Rmd
another points system

points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)

o1 <- replicate(100,resampling(m,f2017,points=points1))
plot(table(o1))

o2 <- replicate(100,resampling(m,f2017,points=points2))
plot(table(o2))

table(o1)
table(o2)
```

>>>>

points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)
points3 <- c(1, 1,1,1,1,1,0,0,0,0,0)

o1 <- replicate(400,resampling(m,f2017,points=points1))
o2 <- replicate(400,resampling(m,f2017,points=points2))
o3 <- replicate(400,resampling(m,f2017,points=points3))

plot(table(o1))
plot(table(o2))
plot(table(o3))

table(o1)
table(o2)
table(o3)
```

and, just for comparison, a stupid one:

```{r,cache=TRUE}
points4 <- c(1, 0,1,2,3,1,0,6,9,0,3)

o4 <- replicate(400,resampling(m,f2017,points=points4))
table(o4)
```
